PK object batch mode trial

### 2023-06-22 data-raw/batchMode_trial_gpm.Rmd
Revised plotting method for observations

my_predata <- subset(cvt,
                     chemicals_analyzed.dsstox_substance_id %in% c("DTXSID0020442",
                                                                   "DTXSID2021731"))

@@

my_coefs_update <- coef(my_pk)
my_pred_update <- predict(my_pk,
                          exclude = TRUE, # add the "exclude" column to output
                          use_scale_conc = FALSE)

my_ndf <- my_pk$data

@@

my_pred_update %>%
  filter(model == "model_2comp",
         Route == "oral",
         Species == "rat", # hamster has a Fgutabs of zero
         method == "L-BFGS-B") %>%
  View("predicted_update")

my_coefs_update %>%
  filter(model == "model_flat",
         Species == "rat",
         method == "L-BFGS-B") %>%
  View("coef_update")

@@

```{r remaining_methods}
# residuals()
# plot()
# 
# get_tkstats()

>>>>

my_predata <- subset(cvt,
                     chemicals_analyzed.dsstox_substance_id %in% c("DTXSID0020442",
                                                                   "DTXSID2021731"))
```

@@

my_coefs_update <- coef(my_pk)
my_pred_update <- predict(my_pk,
                          exclude = TRUE, # add the "exclude" column to output
                          use_scale_conc = TRUE)

@@

@@

```{r plotting_method}
# Experimenting with what works with my_ndf
# 
my_ndf <- my_pk$data

my_ndf %>%
  filter(Chemical %in% "DTXSID0020442", Species %in% "rat") %>%
  mutate(Dose = factor(Dose),
         Reference = factor(Reference),
         Detect_int = as.character(Detect)
         ) %>%
  ggplot(aes(
    x = Time_trans,
    y = Conc_trans,
    color = Dose,
    shape = Reference
  )) +
  geom_point(aes(
    fill = Dose,
    alpha = Detect_int
  )) +
  geom_point() +
  scale_shape_manual(values = 21:25) +
  scale_alpha_manual(values = c("FALSE" = 0, "TRUE" = 1),
                     breaks = c("TRUE", "FALSE"),
                     name = "Detect") +
  guides(shape = guide_legend(override.aes = list(fill = "black")),
         alpha = guide_legend(override.aes = list(alpha = 1,
                                                  fill = c("black", "white"),
                                                  color = "black",
                                                  shape = 21))) +
  facet_grid(rows = vars(Detect), # This is just for illustrative purposes, this would be Routes
             cols = vars(Route)) +
  theme_bw()
# Need to find a way to make this vectorized...
# probably within a mutate and map function

```{r remaining_methods}
# plot()
# 
# get_tkstats()
